---
title: "1Da Cross-selling in banking challenge - Alessia / Jenni"
output: html_notebook
---
We are working with a dataset from a czech bank. 

Below we have loaded all the packages and data as well as organized and sturctured it so we can work with it.
loading all packages and data
```{r}
library(tidyverse)
library(tidymodels)
library(ggmosaic)
library(ggalluvial)
library(rpart)
library(rpart.plot)
library(gridExtra)
library(usethis)
library(ggplot2)

account <- read.csv('./account.csv', sep = ";")
card <- read.csv('./card.csv', sep = ";")
client <- read.csv('./client.csv', sep = ";")
disp <- read.csv('./disp.csv', sep = ";")
district <- read.csv('./district.csv', sep = ';')
loan <- read.csv('./loan.csv', sep = ";")
order <- read.csv('./order.csv', sep = ";")
trans <- read.csv('./trans.csv', sep = ";")

```

separate in columns
```{r}
#update 02.10.2021: we found out that there is an easier way to split the csv into columns with the sep = ";"
#split up the lists in a form
# account <- account %>%
#   separate(account_id.district_id.frequency.date, c("account_id","district_id",'frequency', 'date'), ";")
#   colnames(account)[3] <- 'frequency_issuance'
# 
# card <- card %>%
#   separate(card_id.disp_id.type.issued, c('card_id', 'disp_id', 'type_of_card', 'issued'),';')
# 
# client <- client %>%
#   separate(client_id.birth_number.district_id, c('client_id','birth_num','district_id'),';')
# 
 # district <- district %>%
 #   separate(A1.A2.A3.A4.A5.A6.A7.A8.A9.A10.A11.A12.A13.A14.A15.A16, c('district_code','district_name','region','no_of_inhabitants','no_of_municipalities_with_inhabitants_<_499','no_of_municipalities_with_inhabitants_500-1999','no_of_municipalities_with_inhabitants_2000-9999','no_of_municipalities_with_inhabitants_>10000','no_of_cities','ratio_of_urban_inhabitants','avg_salary','unemploymant_rate_95','unemploymant_rate_96','no_of_enterpreneurs_per_1000_inhabitants','no_of_commited_crimes_95','no_of_commited_crimes_96'),';')
# 
# disp <- disp %>%
#   separate(disp_id.client_id.account_id.type, c('disp_id','client_id','account_id','type_of_disposition'),';')
# 
# loan <- loan %>%
#   separate(loan_id.account_id.date.amount.duration.payments.status,c('loan_id','account_id','date','amount','duration','monthly_payments','status'),';')
# 
# order <- order %>%
#   separate(order_id.account_id.bank_to.account_to.amount.k_symbol,c('order_id','account_id','bank_to','account_to','amount','k_symbol'),';')
# 
# trans <- trans %>%
#   separate(trans_id.account_id.date.type.operation.amount.balance.k_symbol.bank.account,c('trans_id','account_id','date','type','operation','amount','balance','k_symbol','bank','account'),';')

```

clean/organize account
```{r}

#reformat frequency_issuance into 3 new columns
account <- account %>%
  mutate(issuance_monthly = case_when(
    endsWith(frequency, 'MESICNE') ~ 1,
    TRUE ~ 0)
  )

account <- account %>%
  mutate(issuance_weekly = case_when(
    endsWith(frequency, 'TYDNE') ~ 1,
    TRUE ~ 0)
  )

account <- account %>%
  mutate(issuance_transaction = case_when(
    endsWith(frequency, 'PO OBRATU') ~ 1,
    TRUE ~ 0)
  )


#reformat date
account$date_ymd <- format(as.Date(as.character(account$date), "%y%m%d"), "19%y/%m/%d") 

# account <- account %>%
#   select(-date)

#factorize variables
account <- account %>% 
  mutate (frequency = as_factor(frequency), 
          issuance_monthly = as_factor(issuance_monthly), 
          issuance_weekly = as_factor(issuance_weekly), 
          issuance_transaction = as_factor(issuance_transaction),
          date_ymd = as.Date(date_ymd)
          )

#str(account)
```

clean/organize card
```{r}

#reformat type_of_card into 3 new columns
card <- card %>%
  mutate(junior_card = case_when(
    type == 'junior' ~ 1,
    TRUE ~ 0)
  )

card <- card %>%
  mutate(classic_card = case_when(
    type == 'classic' ~ 1,
    TRUE ~ 0)
  )

card <- card %>%
  mutate(gold_card = case_when(
    type == 'gold' ~ 1,
    TRUE ~ 0)
  )

#reformat date
card$issued_date <- format(as.Date(as.character(card$issued), "%y%m%d"), "19%y/%m/%d")
#card <- card %>%
  #select(-issued)




#factorize variables
card <- card %>%
  mutate(type = as_factor(type), 
         junior_card = as_factor(junior_card), 
         classic_card = as_factor(classic_card),
         gold_card = as_factor(gold_card),
         issued_date = as.Date(issued_date)
         )

#str(card)

  
```

clean/organize client (Dani fragen)
```{r}

#reformat birth_number

client <- client %>%
  mutate(month = substr(birth_number, 3, 4)) %>%
  mutate(month = strtoi(month))

client <- client %>%
  mutate(gender = case_when(
    month > 12 ~ 'f',
    TRUE ~ 'm')
  )

client <- client %>%
  mutate(birth_number = as.numeric(birth_number))

client <- client %>%
  mutate(birth_number = case_when(
    month > 12 ~ birth_number - 5000,
    TRUE ~ birth_number)
  )



client$birthday <- format(as.Date(as.character(client$birth_number), "%y%m%d"), "19%y/%m/%d")
# client <- client %>%
#   select(-birth_number)

#factorize variables
client <- client %>%
  mutate(district_id = as_factor(district_id), 
         gender = as_factor(gender),
         birthday = as.Date(birthday)
         )

library(eeptools)
x <- as.Date(c("1998-01-01"))


client$age <- floor(age_calc(as.Date(client$birthday),x, units = "years"))

# client <- client %>%
#   mutate(age = 
#     
#   )

#str(client)
  
```

birthday proper shape
```{r}
client <- client %>%
  mutate(
    birth_number = birth_number + 19000000
  )

# client <- client %>%
#   birth_number += '19' 
```

clean/organize disp
```{r}

#reformat type into 2 new columns
disp <- disp %>%
  mutate(owner = case_when(
    type == 'OWNER' ~ 1,
    TRUE ~ 0)
  )
disp <- disp %>%
  mutate(disponent = case_when(
    type == 'DISPONENT' ~ 1,
    TRUE ~ 0)
  )

#factorize variables
disp <- disp %>%
  mutate(type = as_factor(type), 
         owner = as_factor(owner), 
         disponent = as_factor(disponent)
         )

#str(disp)
```

clean/organize district
```{r}

#rename coluns
names(district) <- c('district_id', 'district_name', 'region', 'habitants', 'municipalities<499',
                     'municipalities<500-1000', 'municipalities<2000-9999', 'municipalities>10000', 'cities',
                     'ratio_urban_inhabitants', 'average_salary', 'unemployment_rate_1995', 'unemployment_rate_1996',
                     'enterpreneurs_per_1000', 'crimes_1995', 'crimes_1996')

#factorize variables
district <- district %>%
  mutate(district_name = as_factor(district_name), region = as_factor(region))

#change datatype to numeric/int
district <- district %>% 
  mutate(unemployment_rate_1995 = as.numeric(unemployment_rate_1995), 
         enterpreneurs_per_1000 = strtoi(enterpreneurs_per_1000), 
         crimes_1995 = strtoi(crimes_1995)
         )

#str(district)

```

clean/organize loan
```{r}

#reformat date
loan$date_issued <- format(as.Date(as.character(loan$date), "%y%m%d"), "19%y/%m/%d")
loan <- loan %>%
  select(-date)

#reformat status into 4 new columns
loan <- loan %>%
  mutate(in_debt = case_when(
    status == 'D' ~ 1,
    TRUE ~ 0)
  )

loan <- loan %>%
  mutate(ok_so_far= case_when(
    status == 'C' ~ 1,
     TRUE ~ 0)
  )

loan <- loan %>%
  mutate(loan_not_payed= case_when(
    status == 'B'~ 1,
    TRUE ~ 0)
  )

loan <- loan %>%
  mutate(payed_off= case_when(
    status == 'A'~ 1,
    TRUE ~ 0)
  )

#factorize variables
loan <- loan %>%
  mutate(duration = as_factor(duration), 
         status = as_factor(status),
         in_debt = as_factor(in_debt), 
         ok_so_far = as_factor(ok_so_far), 
         loan_not_payed = as_factor(loan_not_payed), 
         payed_off = as_factor(payed_off),
         date_issued = as.Date(date_issued)
         )


#str(loan)

```

clean/organize order
```{r}

#reformat k_symbol into 4 new columns
order <- order %>%
  mutate(insurrance_payment = case_when(
    k_symbol == 'POJISTNE' ~ 1,
    TRUE ~ 0)
  )

order <- order %>%
  mutate(household = case_when(
    k_symbol == 'SIPO' ~ 1,
    TRUE ~ 0)
  )

order <- order %>%
  mutate(for_leasing = case_when(
    k_symbol == 'LEASING' ~ 1,
    TRUE ~ 0)
  )

order <- order %>%
  mutate(loan_payment = case_when(
    k_symbol == 'UVER' ~ 1,
    TRUE ~ 0)
  )

#factorize variables
order <- order %>%
  mutate(bank_to = as_factor(bank_to), 
         k_symbol = as_factor(k_symbol), 
         insurrance_payment = as_factor(insurrance_payment), 
         household = as_factor(household), 
         for_leasing = as_factor(for_leasing), 
         loan_payment = as_factor(loan_payment)
         )

#str(order)
```

clean/organize trans
```{r}

#reformat date
trans$date_dmy <- format(as.Date(as.character(trans$date), "%y%m%d"), "19%y/%m/%d")

#reformat type into 2 new columns
trans <- trans %>%
  mutate(credit = case_when(
    type == 'PRIJEM' ~ 1,
    TRUE ~ 0)
  )

trans <- trans %>%
  mutate(withdrawal = case_when(
    type == 'VYDAJ' ~ 1,
    TRUE ~ 0)
  )

#reformat operation into 5 new columns
trans <- trans %>%
  mutate(creditcard_wd = case_when(
    operation == 'VYBER KARTOU' ~ 1,
    TRUE ~ 0)
  )
  
trans <- trans %>%
  mutate(credit_cash = case_when(
    operation == 'VKLAD' ~ 1,
    TRUE ~ 0)
  )

trans <- trans %>%
  mutate(col_from_other_bank = case_when(
    operation == 'PREVOD Z UCTU' ~ 1, 
    TRUE ~ 0)
  )

trans <- trans %>%
  mutate(wd_cash = case_when(
    operation == 'VYBER' ~ 1,
    TRUE ~ 0)
  )

trans <- trans %>%
  mutate(rem_to_other_bank = case_when(
    operation == 'PREVOD NA UCET' ~ 1,
    TRUE ~ 0)
  )

#reformat k_symbol into 7 new columns
trans <- trans %>%
  mutate(ks_insurrance_payment = case_when(
    k_symbol == 'POJISTNE' ~ 1,
    TRUE ~ 0)
  )

trans <- trans %>%
  mutate(ks_payment_of_statement = case_when(
    k_symbol == 'SLUZBY' ~ 1,
    TRUE ~ 0)
  )

trans <- trans %>%
  mutate(ks_interest_credit = case_when(
    k_symbol == 'UROK' ~ 1,
    TRUE ~ 0)
  )

trans <- trans %>%
  mutate(ks_interest_if_n_balance = case_when(
    k_symbol == 'SANKC. UROK' ~ 1,
    TRUE ~ 0)
  )

trans <- trans %>%
  mutate(ks_household = case_when(
    k_symbol == 'SIPO' ~ 1,
    TRUE ~ 0)
  )

trans <- trans %>%
  mutate(ks_old_age_pension = case_when(
    k_symbol == 'DUCHOD' ~ 1,
    TRUE ~ 0)
  )

trans <- trans %>%
  mutate(ks_loan_payment = case_when(
    k_symbol == 'UVER' ~ 1,
    TRUE ~ 0)
  )

#factorize variables
trans <- trans %>%
  mutate(type = as_factor(type),
         credit = as_factor(credit), 
         withdrawal = as_factor(withdrawal), 
         creditcard_wd = as_factor(creditcard_wd),
         operation = as_factor(operation), 
         credit_cash = as_factor(credit_cash), 
         col_from_other_bank = as_factor(col_from_other_bank), 
         wd_cash = as_factor(wd_cash), 
         rem_to_other_bank = as_factor(rem_to_other_bank), 
         ks_insurrance_payment = as_factor(ks_insurrance_payment),
         k_symbol = as_factor(k_symbol), 
         ks_insurrance_payment = as_factor(ks_insurrance_payment),
         ks_payment_of_statement = as_factor(ks_payment_of_statement), 
         ks_interest_credit = as_factor(ks_interest_credit), 
         ks_interest_if_n_balance = as_factor(ks_interest_if_n_balance), 
         ks_household = as_factor(ks_household),
         ks_old_age_pension = as_factor(ks_old_age_pension), 
         ks_loan_payment = as_factor(ks_loan_payment),
         date_dmy = as.Date(date_dmy)
         )

#str(trans)

```

Bring together client and disp
```{r}
client_disp <- full_join(
    disp,client, by = 'client_id'
)

client_disp <- full_join(
  client_disp, card, by = 'disp_id'
)
```

Fragestellung Recherche Jenni

Quick overview research to get to know the outlines of the dataset and decide where to go deeper.


First i wanted to see the genderdistribution of the clients.

As we can see in the Plot below, there are slightly less women than man, but over all the gender is pretty balanced out.
```{r}
client_gender_j <-ggplot(
  client, aes(x = gender, fill = gender))+
  geom_bar()+
  ggtitle('\nClients spread on gender\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )+
  labs( y= '\nNumber of Clients\n', x = '\nGender\n')
client_gender_j

```

```{r}
client_owner_j <-ggplot(
  client_disp, aes(x = gender,fill = type))+
  geom_bar()+
  ggtitle('\nOwner/Disponent spread on gender\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )+
  labs( y= '\nNumber of Clients\n', x = '\nGender\n')
client_owner_j
```


The general information of the Age of the clients is a good base information as well.

We gan see in the plot below most clients are between 20 and 55 years old. 

```{r}
client_age_j <- ggplot(
  client, aes(x = age, colour = gender))+
  #geom_bar(alpha = 0.5)+
  geom_density()+
  ggtitle('\nClientspread on age, separated by gender\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )+
  labs( y= '\ndensity\n', x = '\nAge\n')
  
client_age_j
```




```{r}
card_type_j <- ggplot(
  card, aes(x = type, fill = type))+
  geom_bar()+
  ggtitle('\nSpread of card types\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )
  
card_type_j


```


```{r}
card_type_g_j <- ggplot(
  card, aes(x = type, fill = gender))+
  geom_bar()+
  ggtitle('\nSpread of card types\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )
  
card_type_g_j




```







