---
title: "1Da Cross-selling in banking challenge - Alessia / Jenni"
output: html_notebook
---
We are working with a dataset from a czech bank. 

Below we have loaded all the packages and data as well as organized and sturctured it so we can work with it.
loading all packages and data
```{r}
library(tidyverse)
library(tidymodels)
library(ggmosaic)
library(ggalluvial)
library(rpart)
library(rpart.plot)
library(gridExtra)
library(usethis)
library(ggplot2)
library(dplyr)
```

```{r}

account <- read.csv('./account.csv', sep = ";")
card <- read.csv('./card.csv', sep = ";")
client <- read.csv('./client.csv', sep = ";")
disp <- read.csv('./disp.csv', sep = ";")
district <- read.csv('./district.csv', sep = ';')
loan <- read.csv('./loan.csv', sep = ";")
order <- read.csv('./order.csv', sep = ";")
trans <- read.csv('./trans.csv', sep = ";")

```

clean/organize account
```{r}

#reformat date
account$date_ymd <- format(as.Date(as.character(account$date), "%y%m%d"), "19%y/%m/%d") 

account <- account %>%
  select(-date)

#factorize variables
account <- account %>% 
  mutate (frequency = as_factor(frequency), 
          date_ymd = as.Date(date_ymd)
          ) %>%
  mutate(frequency = case_when(
    frequency == 'POPLATEK MESICNE' ~ 'monthly issuance',
    frequency == 'POPLATEK TYDNE' ~ 'weekly issuance',
    frequency == 'POPLATEK PO OBRATU' ~ 'issuance after transaction'
  ))

```

clean/organize card
```{r}

#reformat date
card$issued_date <- format(as.Date(as.character(card$issued), "%y%m%d"), "19%y/%m/%d")

#factorize variables
card <- card %>%
  mutate(type = as_factor(type), 
         issued_date = as.Date(issued_date)
         )
  
```

clean/organize client (Dani fragen)
```{r}

#reformat birth_number

client <- client %>%
  mutate(month = substr(birth_number, 3, 4)) %>%
  mutate(month = strtoi(month))

client <- client %>%
  mutate(gender = case_when(
    month > 12 ~ 'f',
    TRUE ~ 'm')
  )

client <- client %>%
  mutate(birth_number = as.numeric(birth_number))

client <- client %>%
  mutate(birth_number = case_when(
    month > 12 ~ birth_number - 5000,
    TRUE ~ birth_number)
  )



client$birthday <- format(as.Date(as.character(client$birth_number), "%y%m%d"), "19%y/%m/%d")

#factorize variables
client <- client %>%
  mutate(district_id = as_factor(district_id), 
         gender = as_factor(gender),
         birthday = as.Date(birthday)
         )
project_date = '1998/1/1'

library(eeptools)
x <- as.Date(c("1998-01-01"))


client$age <- floor(age_calc(as.Date(client$birthday),x, units = "years"))

library(eeptools)
x <- as.Date(c("1998-01-01"))


client$age <- floor(age_calc(as.Date(client$birthday),x, units = "years"))

```

birthday proper shape
```{r}
client <- client %>%
  mutate(
    birth_number = birth_number + 19000000
  )

```

clean/organize disp
```{r}

#factorize variables
disp <- disp %>%
  mutate(type = as_factor(type)
         )

```

clean/organize district
```{r}

#rename coluns
names(district) <- c('district_id', 'district_name', 'region', 'habitants', 'municipalities<499',
                     'municipalities<500-1000', 'municipalities<2000-9999', 'municipalities>10000', 'cities',
                     'ratio_urban_inhabitants', 'average_salary', 'unemployment_rate_1995', 'unemployment_rate_1996',
                     'enterpreneurs_per_1000', 'crimes_1995', 'crimes_1996')

#factorize variables
district <- district %>%
  mutate(district_name = as_factor(district_name), region = as_factor(region))

#change datatype to numeric/int
district <- district %>% 
  mutate(unemployment_rate_1995 = as.numeric(unemployment_rate_1995), 
         enterpreneurs_per_1000 = strtoi(enterpreneurs_per_1000), 
         crimes_1995 = strtoi(crimes_1995)
         )

#str(district)

```

clean/organize loan
```{r}

#reformat date
loan$date_issued <- format(as.Date(as.character(loan$date), "%y%m%d"), "19%y/%m/%d")
loan <- loan %>%
  select(-date)


#factorize variables
loan <- loan %>%
  mutate(duration = as_factor(duration), 
         status = as_factor(status),
         date_issued = as.Date(date_issued)
         )

```

clean/organize order
```{r}

#factorize variables
order <- order %>%
  mutate(bank_to = as_factor(bank_to), 
         k_symbol = as_factor(k_symbol)
         )


order <- order %>%
  mutate(k_symbol = case_when(
    k_symbol == 'POJISTNE' ~ 'issurance payment',
    k_symbol == 'SIPO' ~ 'household',
    k_symbol == 'LEASING' ~ 'leasing',
    k_symbol == 'UVER' ~ 'loan payment'
  )
    
  )
#str(order)
```

clean/organize trans
```{r}

#reformat date
trans$date_dmy <- format(as.Date(as.character(trans$date), "%y%m%d"), "19%y/%m/%d")

trans <- trans %>%
  select(-date)

#factorize variables
trans <- trans %>%
  mutate(type = as_factor(type),
         operation = as_factor(operation),
         k_symbol = as_factor(k_symbol),
         date_dmy = as.Date(date_dmy)
         )

trans <- trans %>%
  mutate(type = case_when(
    type == 'PRIJEM' ~ 'credit',
    type == 'VYDAJ' ~ 'withdrawal',
    type == 'VYBER' ~ 'withdrawal in cash'
  )) %>%
  mutate(operation = case_when(
    operation == 'VYBER KARTOU' ~ 'credit card withdrawal',
    operation == 'VKLAD' ~ 'credit in cash',
    operation == 'PREVOD Z UCTU' ~ 'collection from other bank',
    operation == 'VYBER' ~ 'withdrawal in cash',
    operation == 'PREVOD NA UCET' ~ 'remittance to other bank'
  )) %>%
  mutate(k_symbol = case_when(
    k_symbol == 'POJISTNE' ~ 'insurrance payment',
    k_symbol == 'SLUZBY' ~ 'payment for statement',
    k_symbol == 'UROK' ~ 'interest credited',
    k_symbol == 'SIPO' ~ 'hosehold',
    k_symbol == 'DUCHOD' ~ 'old-age pension',
    k_symbol == 'UVER' ~ 'loan payment'
  ))


```

Bring together client and disp
```{r}
client_disp <- full_join(
    disp,client, by = 'client_id'
) 

client_disp <- full_join(
  client_disp, card, by = 'disp_id'
)

client_disp <- client_disp %>%
  rename(
    type_client = type.x,
    type_card = type.y,
    card_issued = issued_date
  ) %>%
  select(
    - birth_number,
    - month,
    - issued
  )


#gender count aller clients
gender_group <- client_disp %>%
 count(gender)
gender_group

#type count aller clients
gen_client_group <- client_disp %>%
  count(type_client)
gen_client_group

#gender count nach type
gen_client_test<- client_disp %>%
  group_by(gender) %>%
  count(type_client)
gen_client_test

#herausfinden ob 1 client mehrere accounts

# gender spread czeck republik 1998 female 51.37% https://data.worldbank.org/indicator/SP.POP.TOTL.FE.ZS?end=1998&locations=CZ&start=1998
```



Fragestellung Recherche Jenni

Quick overview research to get to know the outlines of the dataset and decide where to go deeper.


First i wanted to see the genderdistribution of the clients.

As we can see in the Plot below, there are slightly less women than man, but over all the gender is pretty balanced out.
```{r}
client_gender_j <-ggplot(
  client, aes(x = gender, fill = gender))+
  geom_bar()+
  ggtitle('\nClients spread on gender\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )+
  labs( y= '\nNumber of Clients\n', x = '\nGender\n')
client_gender_j

```

```{r}
client_owner_j <-ggplot(
  client_disp, aes(x = type_client,fill = gender ))+
  geom_bar(position ='dodge')+
  ggtitle('\nOwner/Disponent spread on gender\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )+
  geom_text(aes(label = ..count..), stat = "count", position =  position_dodge(width = 0.9), vjust = 2)+
  labs( y= '\nNumber of Clients\n', x = '\nGender\n')
client_owner_j

#weiter untersuchen, wer macht die Überweisungen und altersgruppen
#check mit count

print(count(client_disp))

owner_total <- sum(client_disp$type_client== 'OWNER')
cat('Total OWNER:', owner_total) 

dispo_total <- sum(client_disp$ype_client== 'DISPONENT')
cat('Total DISPONENT: ', dispo_total)

female_client <- sum(client_disp$gender == 'f')
cat('Total female clients: ',female_client)

male_client <- sum(client_disp$gender == 'm')
cat('Total male clients: ',female_client)

print('There is an equal amount of male and female clients. That is very surprising. We will have a deeper look at this.')
# da stimmt etwas nicht. Bei clients sagts es sind 5369 observationen, wenn mann nach gender odrnet sind immer zu viele das erste geschlecht.????


      

```


The general information of the Age of the clients is a good base information as well.

We gan see in the plot below most clients are between 20 and 55 years old. 

```{r}
client_age_j <- ggplot(
  client, aes(x = age, colour = gender))+
  #geom_bar(alpha = 0.5)+
  geom_density()+
  ggtitle('\nClientspread on age, separated by gender\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )+
  labs( y = '\ndensity\n', x = '\nAge\n')
  
client_age_j

age_count <- client %>%
  group_by(gender, age) %>%
  summarise(
    count = n()
  )
age_count


client_age_jl <- ggplot(
  age_count, aes(x = age, colour = gender, y = count))+
  #geom_bar(alpha = 0.5)+
  # geom_point()+
  geom_line()+
  ggtitle('\nClientspread on age, separated by gender\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )
client_age_jl


```




```{r}
card_type_j <- ggplot(
  card, aes(x = type, fill = type))+
  geom_bar()+
  ggtitle('\nSpread of card types\n')+
  geom_text(aes(label = ..count..), stat = "count", position =  position_dodge(width = 0.9), vjust = 2)+
  theme(
    plot.title = element_text(hjust = 0.5)
    )
  
card_type_j

card_type_jx <- ggplot(
  client_disp, aes(x = type_client, fill = gender))+
  geom_bar(position = 'dodge')+
  ggtitle('\nSpread of card types\n')+
  geom_text(aes(label = ..count..), stat = "count", position =  position_dodge(width = 0.9), vjust = 2)+
  theme(
    plot.title = element_text(hjust = 0.5)
    )
  
card_type_jx

```


```{r}
card_type_g_j <- ggplot(
  client_disp, aes(x = type_card, fill = gender))+
  geom_bar(position = 'dodge')+
  ggtitle('\nSpread of card types\n')+
  geom_text(aes(label = ..count..), stat = "count", position =  position_dodge(width = 0.9), vjust = 2)+
  theme(
    plot.title = element_text(hjust = 0.5)
    )
  
card_type_g_j
```

```{r}
card_type_age_g <- ggplot(
  client_disp, aes(x = age, colour = type_card))+
  geom_density(position = 'dodge')+
  ggtitle('\nSpread of card types\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )
card_type_age_g

age_card <- client_disp %>%
  group_by( type_card, age ) %>%
  summarise(
    count = n()
  )
age_card

card_type_age <- ggplot(
  age_card, aes(x = age, y = count, colour = type_card))+
  geom_line(position = 'dodge')+
  ggtitle('\nSpread of card types\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )
  
card_type_age


age_card_m <- filter(client_disp, gender == 'm')
age_card_m

age_card_f <- filter(client_disp, gender == 'f')
age_card_f

age_card_m <- age_card_m %>%
  group_by(age, type_card) %>%
  summarise(
    count = n()
  ) 

age_card_f <- age_card_f %>%
  group_by(age, type_card) %>%
  summarise(
    count = n()
  ) 


card_type_age_m <- ggplot(
  age_card_m, aes(x = age, y = count, colour = type_card))+
  geom_line(position = 'dodge')+
  ggtitle('\nSpread of card types of male clients\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )
  
card_type_age_m

card_type_age_f <- ggplot(
  age_card_f, aes(x = age, y = count, colour = type_card))+
  geom_line(position = 'dodge')+
  ggtitle('\nSpread of card types of female clients\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )
  
card_type_age_f
```


<<<<<<< HEAD
```{r}
# filter by card, make dataframe for each card type

#wenn junior_card is true pipe into new data frame
client_junior <- filter(client_disp , type_card == 'junior')
client_classic <- filter(client_disp , type_card == 'classic')
client_gold <- filter(client_disp , type_card == 'gold')

client_all_cards <- client_disp %>%
  filter(!is.na(type_card))

client_na <- client_disp %>%
  filter(is.na(type_card))

client_na

client_na_junior <- filter(client_na, age <= 23)
client_na_classic_gold <- filter(client_na, age > 23)
```

```{r}
# client_junior$age_card_issued2 <- client_junior$card_issued - client_junior$birthday 
client_junior$age_card_issued <- floor(age_calc(as.Date(client_junior$birthday),client_junior$card_issued, units = "years"))

junior_issued_age_viz <- ggplot( client_junior, aes( x = age_card_issued, fill = gender))+
  geom_bar( position = 'dodge'
  )+
  # geom_density()+
  ggtitle('\nJunior cards issued on age of owner\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )
junior_issued_age_viz

client_na_junior_age_viz <- ggplot(client_na_junior, aes(x=age, fill=gender))+
  geom_bar(position = 'dodge')+
  ggtitle('\npotential junior card clients age spread\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
  )
client_na_junior_age_viz

```

```{r}
client_classic$age_card_issued <- floor(age_calc(as.Date(client_classic$birthday),client_classic$card_issued, units = 'years'))
client_gold$age_card_issued <- floor(age_calc(as.Date(client_gold$birthday),client_gold$card_issued, units = 'years'))

classic_issued_age_viz <- ggplot(client_classic, aes( x = age, fill = gender))+
  geom_bar(position = 'dodge')+
  ggtitle('\nClassic cards issued on age of owner\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )
classic_issued_age_viz

#nehmen wir alle ab 20 zu der gruppe potential classic????????

gold_issued_age_viz <- ggplot(client_gold, aes( x = age, fill = gender))+
  geom_bar(position = 'dodge')+
  ggtitle('\nGold cards issued on age of owner\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )
gold_issued_age_viz

```

```{r}
#join card information to traansactions via account id

cardowner_transactions <- inner_join(client_all_cards, trans, by = 'account_id') %>%
  mutate(trans_credit =
    case_when(
      type == 'credit' ~ 1,
      type != 'credit' ~ 0
    )
  ) %>%
  mutate(trans_withdrawal =
           case_when(
             type == 'withdrawal' ~ 1,
             type != 'withdrawal' ~ 0
           )
  ) %>%
  mutate(
    type = as.factor(type),
    operation = as.factor(operation),
    k_symbol = as.factor(k_symbol),
    bank = as.factor(bank)
  )

junior_card_transactions <- filter(cardowner_transactions, type_card == 'junior')
classic_card_transactions <- filter(cardowner_transactions, type_card == 'classic')
gold_card_transactions <- filter(cardowner_transactions, type_card == 'gold')
```


```{r}
junior_card_transactions_2 <- junior_card_transactions %>%
  group_by(account_id, type) %>%
  summarise(
    count = n()
  ) 
junior_card_transactions_2



```

```{r}

#zuerst durchschnitt pro gender berechnen und dann mean pro gender angeben

junior_type_sum <- junior_card_transactions$type %>%
  summary()

classic_type_sum <- classic_card_transactions$type %>%
  summary()

gold_type_sum <- gold_card_transactions$type %>%
  summary()

print('junior_type')
junior_type_sum
print('classic_type')
classic_type_sum
print('gold_type')
gold_type_sum


#Na untersuchen juniorcard
junior_card_transactions_na <- filter(junior_card_transactions, is.na(type)) 

junior_card_transactions_na_sum <- junior_card_transactions_na$operation %>%
  summary()
junior_card_transactions_na_sum

#na untersuchen classic card
classic_card_transactions_na <- filter(classic_card_transactions, is.na(type)) 

classic_card_transactions_na_sum <- classic_card_transactions_na$operation %>%
  summary()
classic_card_transactions_na_sum

#na untersuchen gold card
gold_card_transactions_na <- filter(gold_card_transactions, is.na(type)) 
```

```{r}
client_gender <-ggplot(
  client, aes(x = gender, fill = gender))+
  geom_bar()+
  ggtitle('\nClients spread on gender\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )+
  labs( y= '\nNumber of Clients\n', x = '\nGender\n')
client_gender

```

The general information of the Age of the clients is a good base information as well.


```{r}
client_age <- ggplot(
  client, aes(x = age,colour = gender))+
  # geom_bar(alpha = 0.5)+
  geom_density()+
  ggtitle('\nClientspread on age, separated by gender\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )+
  labs( y= '\ndensity\n', x = '\nAge\n')
  
client_age
```

```{r}
card_type <- ggplot(
  card, aes(x = type, fill = type))+
  geom_bar()+
  ggtitle('\nSpread of card types\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
    )
  
card_type


gold_card_transactions_na_sum <- gold_card_transactions_na$operation %>%
  summary()
gold_card_transactions_na_sum

```


```{r}

junior_trans_viz <- ggplot(junior_card_transactions, aes( x = type, fill = gender))+
  geom_bar(position = 'dodge')+
  ggtitle('\nCredit compared to withdrawals Junior Card\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
  )
junior_trans_viz




classic_trans_viz <- ggplot(classic_card_transactions, aes( x = type, fill = gender))+
  geom_bar(position = 'dodge')+
  ggtitle('\nCredit compared to withdrawals classic card\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
  )
classic_trans_viz

gold_trans_viz <- ggplot(gold_card_transactions, aes( x = type, fill = gender))+
  geom_bar(position = 'dodge')+
  ggtitle('\nCredit compared to withdrawals gold card\n')+
  theme(
    plot.title = element_text(hjust = 0.5)
  )
gold_trans_viz
```


Join tables:
1) Left join of account with disp to df_account_disp. Then left join df_account_disp with client to df_account_disp_client. 
```{r}
df_account_disp <- left_join(account, disp, by = 'account_id') 
df_account_disp_client <- left_join(df_account_disp, client, by = 'client_id') %>%
  select(-birth_number, -birthday) %>%
  rename(
    district_account = district_id.x,
    date_account = date_ymd,
    district_client = district_id.y,
  )
```

2) Left join order with df_account_disp_client to df_order_account_client_disp.
```{r}
df_order_account_client_disp <- left_join(order, df_account_disp_client, by = "account_id")
```

3) Left join loan with df_account_disp_client to df_loan_account_client_disp.
```{r}
df_loan_account_client_disp <- left_join(loan, df_account_disp_client, by = "account_id")
```

4) Left join trans with df_account_disp_client to df_trans_account_client_disp.
```{r}
df_trans_account_client_disp <- left_join(trans, df_account_disp_client, by = "account_id") %>%
  rename(
    trans_type = type.x,
    account_type = type.y
  )
```

Analyse the probability of clients age
Visualize the gender difference
```{r}
#density plot, women and men separated
df_account_disp_client %>% ggplot(aes(x = age, color = gender)) +
    geom_density(size = 1) + xlab('Age of clients')
```

Visualize the number of accounts according to the clients age with different kinds of bar charts
```{r}
#bar chart, one bar for each age
df_account_disp_client %>% ggplot(aes(x = age)) + geom_bar() + scale_fill_brewer(palette = "Paired") 

#bar chart, women and men separated, one bar for each age
df_account_disp_client %>% ggplot(aes(x = age, fill = gender)) + geom_bar(position = 'dodge') +
         scale_fill_brewer(palette = "Paired") + xlab('Age of clients')

#stacked bar chart, women and men separated, one bar for each age
df_account_disp_client %>% ggplot(aes(x = age, fill = gender)) + geom_bar() +
         scale_fill_brewer(palette = "Paired") + xlab('Age of clients')

#two bar charts, women and men separated, each age one bar
df_account_disp_client %>% ggplot(aes(x = age, fill = gender)) + geom_bar() +
         scale_fill_brewer(palette = "Paired") + facet_wrap(~ gender) + xlab('Age of clients')

#coordination flipped bar chart, omen and men separated, one bar for each age
df_account_disp_client %>% ggplot(aes(x = age, fill = gender)) + geom_bar() + coord_flip() +
         scale_fill_brewer(palette = "Paired") + xlab('Age of clients')

#coordination flipped bar chart, omen and men separated, one bar for each age, in percentage
df_account_disp_client %>% ggplot(aes(x = age, fill = gender)) + geom_bar(position = 'fill') +
  coord_flip() + geom_hline(yintercept = 0.5, color = 'red', size = 0.75) +
  scale_fill_brewer(palette = "Paired") + xlab('Age of clients')

```

Analysis of the "turning points" in the top bar charts: Count the number of accounts a for example 16 year old client, female client and male client has. I a next step analyse the one year older client. 
```{r}
#turning points in age
#in general
nr1 <- df_account_disp_client %>%
  filter(age == 16) %>%
  nrow()
print('number of account of 16 year old clients')
nr1

nr2 <- df_account_disp_client %>%
  filter(age == 17) %>%
  nrow()
print('number of account of 17 year old clients')
nr2

nr3 <- df_account_disp_client %>%
  filter(age == 58) %>%
  nrow()
print('number of account of 58 year old clients')
nr3

nr4 <- df_account_disp_client %>%
  filter(age == 59) %>%
  nrow()
print('number of account of 59 year old clients')
nr4

nr5 <- df_account_disp_client %>%
  filter(age == 79) %>%
  nrow()
print('number of account of 79 year old clients')
nr5

nr6 <- df_account_disp_client %>%
  filter(age == 80) %>%
  nrow()
print('number of account of 80 year old clients')
nr6

#turning points in age
#for women
df_account_disp_client_w <- df_account_disp_client %>%
  filter(gender == 'f')

nrw1 <- df_account_disp_client_w %>%
  filter(age == 16) %>%
  nrow()
print('number of account of 16 year old female clients')
nrw1

nrw2 <- df_account_disp_client_w %>%
  filter(age == 17) %>%
  nrow()
print('number of account of 17 year old female clients')
nrw2

nrw3 <- df_account_disp_client_w %>%
  filter(age == 58) %>%
  nrow()
print('number of account of 58 year old female clients')
nrw3

nrw4 <- df_account_disp_client_w %>%
  filter(age == 59) %>%
  nrow()
print('number of account of 59 year old female clients')
nrw4

nrw5 <- df_account_disp_client_w %>%
  filter(age == 79) %>%
  nrow()
print('number of account of 79 year old female clients')
nrw5

nrw6 <- df_account_disp_client_w %>%
  filter(age == 80) %>%
  nrow()
print('number of account of 80 year old female clients')
nrw6

#for men
df_account_disp_client_m <- df_account_disp_client %>%
  filter(gender == 'm')

nrm1 <- df_account_disp_client_m %>%
  filter(age == 16) %>%
  nrow()
print('number of account of 16 year old male clients')
nrm1

nrm2 <- df_account_disp_client_m %>%
  filter(age == 17) %>%
  nrow()
print('number of account of 17 year old male clients')
nrm2

nrm3 <- df_account_disp_client_m %>%
  filter(age == 62) %>%
  nrow()
print('number of account of 62 year old male clients')
nrm3

nrm4 <- df_account_disp_client_m %>%
  filter(age == 63) %>%
  nrow()
print('number of account of 63 year old male clients')
nrm4

nrm5 <- df_account_disp_client_m %>%
  filter(age == 79) %>%
  nrow()
print('number of account of 79 year old male clients')
nrm5

nrm6 <- df_account_disp_client_m %>%
  filter(age == 80) %>%
  nrow()
print('number of account of 80 year old male clients')
nrm6
```

Group the clients same sized age groups. The group size is 16. With grouping the clients we are losing some information. But with grouping the clients in different group sizes we would create a misleading chart. 
```{r}
#order the clients by youngest and oldest, youngest is 10, oldest is 86
#group all the clients in 7 different groups
df_account_disp_client <- df_account_disp_client %>%
  mutate(age_grouped = case_when(
    age <= 16 ~ '1-16',
    age <= 32 ~ '17-32',
    age <= 48 ~ '33-48',
    age <= 64 ~ '49-64',
    age <= 72 ~ '65-72',
    age <= 86 ~ '73-86',
    TRUE ~ 'not known'
  ))

#factor the groups
df_account_disp_client <- df_account_disp_client %>% 
  mutate(age_grouped = as_factor(age_grouped))

#order the new age column in a determined way
df_account_disp_client$age_grouped <- 
  ordered(df_account_disp_client$age_grouped, levels = c('1-16', '17-32', '33-48', '49-64', '65-72',
                                                         '73-86'))
```

Visualize the number of accounts according to the clients age with different kinds of bar charts now using the age groups
```{r}
#bar chart, all clients in 7 groups
df_account_disp_client %>% ggplot(aes(x = factor(age_grouped))) + geom_bar() +
  geom_text(aes(label = ..count..), stat = "count", vjust = 1.3, colour = 'white') +
  xlab('Age of clients')

#two bar charts, women and men separated, 7 groups 
df_account_disp_client %>% ggplot(aes(x = age_grouped, fill = gender)) + geom_bar() +
  geom_text(aes(label = ..count..), stat = "count", vjust = 1.3, colour = 'white') +
  scale_fill_brewer(palette = "Paired") + facet_wrap(~ gender)+ xlab('Age of clients')

#bar chart, women and men separated, 7 groups 
df_account_disp_client %>% ggplot(aes(x = age_grouped, fill = gender)) + geom_bar(position = 'dodge') +
  scale_fill_brewer(palette = "Paired") + xlab('Age of clients')

#stacked bar chart, women and men separated, 7 groups 
df_account_disp_client %>% ggplot(aes(x = age_grouped, fill = gender)) + 
  geom_bar() + scale_fill_brewer(palette = "Paired") + 
  geom_text(aes(label = ..count..), stat = "count", vjust = 1.3, colour = 'white', position = 'stack') +
  xlab('Age of clients')

#reorder the age3 column to ascending
df_account_disp_client <- df_account_disp_client %>%
  mutate(age3 = fct_reorder(age_grouped, desc(age_grouped))) 

#coordination flipped bar chart, women and men separated, 7 groups 
df_account_disp_client %>% ggplot(aes(x = age_grouped, fill = gender)) + 
  geom_bar() + scale_fill_brewer(palette = "Paired") + coord_flip() +
  geom_text(aes(label = ..count..), stat = "count", vjust = 1, colour = 'white', position = 'stack') +
  xlab('Age of clients')

#coordination flipped bar chart, women and men separated, 7 groups, in percentage
df_account_disp_client %>% ggplot(aes(x = age_grouped, fill = gender)) + 
  geom_bar(position = 'fill') + scale_fill_brewer(palette = "Paired") + coord_flip() + 
  geom_errorbar(aes(xintercept = x, ymax=0.5, ymin=0.5), color = 'red', size = 1) +
  xlab('Age of clients') + ylab('Density') 

#coordination flipped bar chart, women and men separated, 7 groups, in percentage
df_account_disp_client %>% ggplot(aes(x = age_grouped, fill = gender)) + 
  geom_bar(position = 'fill') + scale_fill_brewer(palette = "Paired") + coord_flip() + 
  geom_hline(yintercept = 0.5, color = 'red', size = 1) +
  xlab('Age of clients') + ylab('Density') 
```

```{r}
#Showing the different account types related to clients age
df_account_disp_client %>% ggplot(aes(x = age, color = type)) +
    geom_density(size = 1) + xlab('Age of clients')

#coordination flipped bar chart, women and men separated, owner and disponent stacked
df_account_disp_client %>% ggplot(aes(x = gender, fill = type)) + 
  geom_bar() + scale_fill_brewer(palette = "Paired") +
  coord_flip() + xlab('Gender of clients')

#coordination flipped bar chart, women and men separated, owner and disponent stacked (probability)
df_account_disp_client %>% ggplot(aes(x = gender, fill = type)) + 
  geom_bar(position = 'fill') + scale_fill_brewer(palette = "Paired") +
  coord_flip() + xlab('Gender of clients')

#coordination flipped bar chart, different age groups, owner and disponent stacked 
df_account_disp_client %>% ggplot(aes(x = age_grouped, fill = type)) + 
  geom_bar() + scale_fill_brewer(palette = "Paired") +
  coord_flip() + xlab('Age of clients')

#coordination flipped bar chart, different age groups, owner and disponent stacked (probability)
df_account_disp_client %>% ggplot(aes(x = age_grouped, fill = type)) + 
  geom_bar(position = 'fill') + scale_fill_brewer(palette = "Paired") +
  coord_flip() + xlab('Age of clients')

#jitter plot showing the different types of clients related to their age
df_account_disp_client %>% ggplot(aes(x = gender, y = age)) + 
  geom_jitter(height = 0, alpha = 0.5, size = 1, width = 0.3, aes(color = type)) +
  xlab('Gender of clients') + ylab('Age of clients') + ggtitle(label = 'Client type related to gender and age')

#jitter plot showing the different types of clients related to their age
df_account_disp_client %>% ggplot(aes(x = gender, y = age)) + 
  geom_jitter(height = 0, alpha = 0.5, size = 1, width = 0.3, aes(color = type)) +
  facet_wrap(~type) +
  xlab('Gender of clients') + ylab('Age of clients') + 
  ggtitle(label = 'Client type related to gender and age')
```
QUESTION: Is there a minimum and/or maximum age of clients being an owner?


```{r}
#I don't know how to handle this plot
df_account_disp_client %>% ggplot(aes(x = date_account, y = age, group = gender, shape = gender)) +
    geom_line() + geom_point()
```

Analyse how many accounts are duplicates
```{r}
nrow(account)

#create data frame duplicate_accounts and print all of those
duplicate_accounts <- df_account_disp_client[duplicated(df_account_disp_client$account_id)|duplicated(df_account_disp_client$account_id, fromLast=TRUE),]
duplicate_accounts

#number of accounts with more than one client
dim(df_account_disp_client[duplicated(df_account_disp_client$account_id),])[1]

#is there an account with more than 2 clients?
table_dup_accounts <- table(duplicate_accounts$account_id)
most_dup_accounts <- names(table_dup_accounts[table_dup_accounts==max(table_dup_accounts)])
#we see, that it is a 1x869 matrix and the number of duplicate accounts is 869 aswell
#so there isn't an account with more than two clients connected

#create data frame unique_accounts with just one client behind
unique_accounts <- anti_join(df_account_disp_client, duplicate_accounts)
unique_accounts
```
ANALYSIS: The clients seem to be partners because there is always a men and a women of the same age (+- 10 years)


Visualize the duplicate accounts
a) All duplicate accounts together
```{r}
#Different account types related to clients age with density plot
duplicate_accounts %>% ggplot(aes(x = age, color = type)) +
    geom_density(size = 1) + xlab('Age of clients')

#Frequency related to age with line plot
df_duplicate_accounts <- duplicate_accounts %>%
  group_by(age, frequency) %>%
  summarise(
    count = n()
  )

df_duplicate_accounts %>% ggplot(aes(x = age, y = count, colour = frequency)) +
  geom_line(position = 'dodge')

#Different account types related to the gender of the clients
duplicate_accounts %>% ggplot(aes(x = gender, fill = type)) + 
  geom_bar() + scale_fill_brewer(palette = "Paired") +
  coord_flip() + xlab('Gender of clients')

#Different account types related to the gender of the clients (probability)
duplicate_accounts %>% ggplot(aes(x = gender, fill = type)) + 
  geom_bar(position = 'fill') + scale_fill_brewer(palette = "Paired") + coord_flip() + 
  xlab('Age of clients') + ylab('Density')
```
ANALYSIS: Obviously there is a 50:50 distribution and a 50% denisity according to the result that there is alyways a men and a women holding the account. 


b) Just the owners
```{r}
#Owners of an account, related to age, separated by gender
owner_duplicate_accounts <- filter(duplicate_accounts, type == 'OWNER')
owner_duplicate_accounts %>% ggplot(aes(x = age, color = gender)) +
    geom_density(size = 1) + xlab('Age of clients')

#Different account types related to the gender of the clients
owner_duplicate_accounts %>% ggplot(aes(x = gender, fill = gender)) + 
  geom_bar() + scale_fill_brewer(palette = "Paired") +
  coord_flip() + xlab('Gender of clients')

#Different account types related to the gender of the clients (probability)
owner_duplicate_accounts %>% ggplot(aes(x = gender, fill = gender)) + 
  geom_bar(position = 'fill') + scale_fill_brewer(palette = "Paired") + coord_flip() + 
  xlab('Age of clients') + ylab('Density')
```
ANALYSIS: In older generations men used to have higher status in family hierarchy whereas in younger generations women seem to be responsible to administrative or financial tasks more often. 
Overall the number of men and women being owner is more or less the same. 


c) Just the disponents
```{r}
#Owners of an account, related to age, separated by gender
disponent_duplicate_accounts <- filter(duplicate_accounts, type == 'DISPONENT')
disponent_duplicate_accounts %>% ggplot(aes(x = age, color = gender)) +
    geom_density(size = 1) + xlab('Age of clients')

#Different account types related to the gender of the clients
disponent_duplicate_accounts %>% ggplot(aes(x = gender, fill = gender)) + 
  geom_bar() + scale_fill_brewer(palette = "Paired") +
  coord_flip() + xlab('Gender of clients')

#Different account types related to the gender of the clients (probability)
disponent_duplicate_accounts %>% ggplot(aes(x = gender, fill = gender)) + 
  geom_bar(position = 'fill') + scale_fill_brewer(palette = "Paired") + coord_flip() + 
  xlab('Age of clients') + ylab('Density')
```
ANALYSIS: The contrary of the top analysis with the owners.


Visualize the unique accounts
```{r}
#Different account types related to clients age
unique_accounts %>% ggplot(aes(x = age, color = type)) +
    geom_density(size = 1) + xlab('Age of clients')

#Density plot for the age of the unique clients, gender separated 
unique_accounts %>% ggplot(aes(x = age, color = gender)) +
    geom_density(size = 1) + xlab('Age of clients')

#Frequency related to age with line plot
df_unique_accounts <- unique_accounts %>%
  group_by(age, frequency) %>%
  summarise(
    count = n()
  )

df_unique_accounts %>% ggplot(aes(x = age, y = count, colour = frequency)) +
  geom_line(position = 'dodge')
```
ANALYSIS: This result is obviously aswell because if just one person holds an account he or she should be owner of the account. 

```{r}
#are there any NA's in colum frequency?
flag_na <- filter(df_account_disp_client, is.na(frequency))
flag_na

#this plot isn't very useful at all
df_account_disp_client %>% ggplot(aes(x = gender, y = age)) + 
  geom_jitter(height = 0, alpha = 0.75, aes(color = frequency))

#this plot isn't very useful at all
df_account_disp_client %>% ggplot(aes(x = date_account, y = age)) + 
  geom_point(aes(colour = frequency)) + 
  geom_smooth(method='lm') + 
  xlab('Date of account') + ylab('Age of clients') + ggtitle(label = 'Account opening relatet to client age')

#this plot shows interesting differences in age for weekly issuance and issuance after transaction
df_account_disp_client %>% ggplot(aes(x = age, color = frequency)) +
    geom_density(size = 1) + xlab('Age of clients')

#this plot shows interesting differences in age for weekly issuance and issuance after transaction
df_account_disp_client %>% ggplot(aes(x = date_account, color = frequency)) +
    geom_density(size = 1) + xlab('Time')

```

```{r}
summary(df_trans_account_client_disp)
```

```{r}
#Density plot for the age of clients related to transition type
df_trans_account_client_disp %>% ggplot(aes(x = age, color = trans_type)) +
    geom_density(size = 1) + xlab('Age of clients')

#Density plot for the time related to transition type
df_trans_account_client_disp %>% ggplot(aes(x = date_dmy, color = trans_type)) +
    geom_density(size = 1) + xlab('Time')

#Density plot for the age of clients related to transition type
df_trans_account_client_disp %>% ggplot(aes(x = age, color = gender)) +
    geom_density(size = 1) + xlab('Age of clients')

#Density plot for the time related to transition type
df_trans_account_client_disp %>% ggplot(aes(x = date_dmy, color = gender)) +
    geom_density(size = 1) + xlab('Time')

#Frequency related to age with line plot
df_unique_accounts <- unique_accounts %>%
  group_by(age, frequency) %>%
  summarise(
    count = n()
  )

#NEWEST
df_trans <- df_trans_account_client_disp %>%
  group_by(account_id, date_dmy, trans_type, operation, age)

df_trans %>% ggplot(aes(x = date_dmy, y = age, colour = trans_type)) +
  geom_line(position = 'dodge')

df_trans %>% ggplot(aes(x = date_dmy, y = age, colour = operation)) +
  geom_line(position = 'dodge')

```




